EldersAIR: manuscript tables/figures

### 2022-08-29 manuscript_tables_figures.Rmd
Update restrictive/obstructive summary results

>>>>

```{r}
obstruction_data <- elders_cleaned_dataset_by_visit %>% 
  arrange(home, adult_id_num, winter_id, sampling_visit) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         obstruction = if_else(fev1_fvc_ratio < 0.7, "Yes", "No")) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction, spiro_status, bp_sys, bp_dia) %>%
  filter(winter_id == 1) %>% 
  filter(spiro_status == "Acceptable") %>% 
  group_by(area, adult_id_num) %>% 
  mutate(obs_any = if_else(obstruction == "Yes" | lead(obstruction) == "Yes", "Yes", "No"),
         obs_any = if_else(is.na(obs_any), obstruction, obs_any)) %>% 
  ungroup() %>% 
  distinct(area, adult_id_num, .keep_all = TRUE)  
  count(obs_any)
obstruction_data

hypertension_pft_data <- elders_cleaned_dataset_by_visit %>% 
  arrange(area, home, adult_id_num, winter_id, sampling_visit) %>% 
  mutate(obstruction = if_else(asthma == "Yes" | chronicbronchitis == "Yes" | 
                                 emphysema == "Yes" | copd == "Yes", "Yes", "No")) %>% 
  filter(winter_id == 1) %>% 
  #filter(spiro_status == "Acceptable") %>% 
  group_by(area, adult_id_num) %>% 
  mutate(bp_sys = mean(bp_sys, na.rm = T),
         bp_dia = mean(bp_dia, na.rm = T),
         fvc_pp = mean(fvc_pp, na.rm = T),
         fev1_pp = mean(fev1_pp, na.rm = T),
         fev1_fvc_ratio = mean(fev1_fvc_ratio, na.rm = T)) %>% 
  mutate(hypertension_calc = if_else(bp_sys >= 140 | bp_dia >= 90, "Yes", "No"),
         fev1_fvc_0.7 = if_else(fev1_fvc_ratio < 0.7, "Yes", "No"),
         fvc_pp_0.8 = if_else(fvc_pp < 80, "Yes", "No"),
         fev1_pp_0.8 = if_else(fev1_pp < 80, "Yes", "No"),
         obstructive = if_else(fev1_pp < 80 & fev1_fvc_ratio < 0.7, "Yes", "No"),
         restrictive = if_else(fev1_pp < 80 & fev1_fvc_ratio > 0.7, "Yes", "No")) %>% 
  ungroup() %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, adult_id_num,
         hypertension, obstruction,
         hypertension_calc, obstructive, spiro_status, bp_sys, bp_dia,
         fev1_fvc_0.7, fvc_pp_0.8, fev1_pp_0.8, restrictive) %>%
  distinct(area, adult_id_num, .keep_all = T) %>% 
  group_by(obstruction) %>% 
  count(obstructive)
hypertension_pft_data
```
